Verifying Demonstrations

### 2020-03-11 paper/DB-Schnorr-UWB.tex
Adds proof sketches (informal proofs) for UWB MITM and anon

There are two questions we must answer about this protocol:
\begin{enumerate}
  \item Can the adversary perform \iac{MITM} attack against the \ac{DHKE}?
  \item Does \(\XDHCL\) break anonymity?
\end{enumerate}

>>>>

There are two questions we must answer about this protocol:
\begin{enumerate}
  \item\label{DBSHW-MITM} Can the adversary perform \iac{MITM} attack against 
    the \ac{DHKE}?
  \item\label{DBSHW-anon} Does \(\XDHCL\) break anonymity?
\end{enumerate}

To answer the first question, by \textcite{Camenisch-phdthesis}, the above 
protocol is \iac{ZKPK}.
In the case of \iac{MITM}, the prover will run the protocol using \(\XDH\) and 
\(\sk\), while the verifier will use \(\XDH'\), possibly modified by the 
adversary.
The adversary's goal is to pass as knowing \(\sk\) and its signature (to 
impersonate real hardware).
The \(\sk\) must be the same \(\sk\) throughout the 
subproofs~\cite{Camenisch-phdthesis}.
In one subprotocol, the prover will prove knowledge of \(\XDH^{\sk}\).
If \(\XDH' \neq \XDH\) used by the verifier is wrong, then by soundness the 
proof will fail.

\(\XDHCL = \XDH^{\sk}\) is simply a representation of \(\sk\) in a randomly 
chosen base~\(\XDH\).
If an adversary can use this to tell one device from another, then the 
adversary can solve the \ac{DDH} problem.
Consider the following reduction.

Assume that \(\adv\) can tell \(\XDH^{\sk}\) from \(\XDH^{\sk'}\) with 
probability \(\frac{1}{2} + \epsilon\) (\ie \(\epsilon\) better than guessing).
We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\).
Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to the adversary, for \(1\leq i\leq 
n\).
Finally, give the adversary the challenge \(g, Y, Z\).
If the adversary recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
\ac{DDH} with the same advantage \(\epsilon\).
